A quantum parallel Markov chain Monte Carlo

### 2022-12-25 main.tex
convergence fig

>>>>

\subsubsection{Ising model}

 \begin{figure}[!t]
	\centering
	\includegraphics[width=0.7\linewidth]{Ising2dFig.pdf}
	\caption{Convergence of log-probability statistic for a independence parallel MCMC samplers targeting an Ising model with uniform correlation $\lambda=1$ and no external field. Larger proposal counts allow discovery of higher probability configurations, albeit with diminishing returns.}\label{fig:ising2d}
\end{figure}
